### 2013-10-18 Rcode/ash.test.rmd
export posterior_dist

set.seed(133)
system.time((beta.ash=ash(ss$betahat,ss$betasd,randomstart=TRUE)))
set.seed(133)
system.time((beta.ash2=oldash(ss$betahat,ss$betasd,auto=TRUE,randomstart=TRUE)))

>>>>

set.seed(133)
system.time((beta.ash=ash(ss$betahat,ss$betasd,prior="uniform",randomstart=TRUE)))
set.seed(133)
system.time((beta.ash2=oldash(ss$betahat,ss$betasd,auto=TRUE,prior="uniform",randomstart=TRUE)))
